A comparison of design-based and model-based approaches for spatial data.

### 2021-10-04 inst/SpatialDVM_Manuscript/SpatialDVM_Manuscript.Rmd
minor graph update.

```{r}
ggplot(data = combo_data_grts, aes(x = n, y = coverage, colour = approach)) +
  geom_hline(yintercept = 0.95) +
  geom_jitter(width = 7) + 
  facet_grid(psill ~ resptype) +
  scale_colour_manual(values = c("mediumpurple1", "mediumpurple4"))
```

>>>>

```{r}
ggplot(data = combo_data_grts, aes(x = n, y = coverage, colour = approach)) +
  geom_hline(yintercept = 0.95) +
  geom_jitter(width = 7) + 
  facet_grid(psill ~ resptype) +
  scale_colour_manual(values = c("mediumpurple1", "mediumpurple4")) +
  theme_bw()
```
